\section{Conclusion}
\label{sec:Conclusion}
\lhead{Conclusion}

In conclusion, I would consider the \textit{Connected.Football} Software Factory project a personal success. While the development of the application and the \textit{Vote4Fun} extension ran into tremendous problems, I have learned to make use of various frameworks, tools and techniques.
\newline
Considering the BOKS model, I was able to enhance my skills in the activities \textit{User Interaction Implementation}, \textit{Software Design} and \textit{Software Implementation}. I am now able to create complex software systems including their interaction with existing and potentially deprecated components and systems. This includes coming up with a design component and software structure as well as test strategies and methods.
\newline
I am furthermore able to understand and develop \textit{React Native} applications and components, including functional, stateless components and the usage of the \textit{recompose} framework. I can utilise \textit{GraphQL} queries and mutations within them and have learned a bit about the usage of the \textit{Firebase} on-boarding system.
\newline
It is now possible for me to make use of \textit{NPM} to import open source packages to use in my own environment. I can make use of them both in \textit{React Native} applications as well as in any other \textit{JavaScript} environment.
\newline
I learned how to make use of Atlassian \textit{Jira}. Using \textit{Jira}, I was able to keep track of all required tasks and tasks assigned to me. It was possible to plan future development, and I hope to make use of the tool in future projects.
\newline
Due to my research, I gained extensive knowledge on the topic of testing \textit{React Native} applications. I am now able to develop and execute tests that interact with a \textit{React Native} application and can understand the results of said tests. This way, I can also start new \textit{React Native} project in a test-driven manner.
\newline
Overall, I have gained a noticeable amount of skills over the course of the project. I consider these skills to be a great asset, both in terms of \textit{React Native} development as well as in general software engineering, and I hope to make use of them in another project soon.